\documentclass[fleqn,usenatbib,useAMS]{mnras}

\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{multicol}
\usepackage{bm}
\usepackage{pdflscape}

\usepackage[T1]{fontenc}
\usepackage{ae,aecompl}

\usepackage{newtxtext,newtxmath}

\title[Relativistic disc lines]{Relativistic lines from thick discs in different spacetimes}

\author[F. Baker, et al.]{F. Baker$^{1}$\thanks{Contact e-mail: \href{mailto:fergus.baker@bristol.ac.uk}{fergus.baker@bristol.ac.uk}}, W. Tarnopolska$^{1}$, and A. J. Young$^{1}$ \\
$^{1}$HH Wills Physics Laboratory, Tyndall Avenue, Bristol BS8 1TL}

\date{Last updated 2024-06-11}

\pubyear{2024}

\begin{document}
\label{firstpage}
\pagerange{\pageref{firstpage}--\pageref{lastpage}}
\maketitle

\begin{abstract}
Abstract will go here
\end{abstract}

\begin{keywords}
keywords -- will -- go -- here
\end{keywords}

\section{Introduction}

An introduction to iron lines and their calculation. Include review articles and describe what has already been done. Specifically note that there are models for thick discs \citep{taylor2018} in standard spacetimes. These can be extended to non-standard spacetimes \citep{abdikamalov2020}. However, these models do not include self-consistently calculated disc illumination. Furthermore, the models are costly to calculate and are only available for a limited range of parameter and spacetimes. We aim to address these shortcomings.

\section{Iron line profiles}

\section{Power law emissivity}

\section{Self-consistent emissivity calculation}

\section{Degenerate iron lines}

\section*{Acknowledgements}

Thanks to various funding bodies and grants.

\section*{Data Availability}
 
The inclusion of a Data Availability Statement is a requirement for articles published in MNRAS. Data Availability Statements provide a standardised format for readers to understand the availability of data underlying the research results described in the article. The statement may refer to original data generated in the course of the study or to third-party data analysed in the article. The statement should describe and provide means of access, where possible, by linking to the data or providing the required accession numbers for the relevant databases or DOIs.

\bibliographystyle{mnras}
\bibliography{line-profiles}

\bsp
\label{lastpage}
\end{document}
